---
title: "Counter Projection - Additional Analyses"
author: "Kathryn Denning"
date: "6/18/2020"
output: 
  html_document:
    code_folding: "hide"
    toc: true
    toc_float: true
    dev: png
  pdf_document:
    dev: cairo_pdf
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---
```{r set-up, include = FALSE}
#loading packages
library(foreign)
library(reshape2)
library(tidyverse)
library(dplyr)
library(car)
library(haven)
library(psych)
library(lmerTest)
library(sjPlot)
library(reshape2)
library(data.table)
library(emmeans)
library(effects)
library(Cairo)
library(tinytex)

#making it round to three decimal places
options(scipen = 999)
knitr::opts_knit$set(dev.args = list(type = "cairo"))

#Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r data import and cleaning initial study, include = FALSE}
#importing data with IP address and lat/long to look for MTurk bots
bot_check <- Import("ppt1_with lat long to check bots.csv") 

bot_check <- bot_check[-c(1,2),,drop = F] 

#importing the data that has been reviewed for completion of PT task
wide_data <- Import("ppt1_fulldata_ptcleanedonly.xlsx") 

#dropping the longer description of each question
wide_dropped1 <- wide_data[-c(1),,drop = F] 

#removing repeat IP addresses since those often indicate bots
#getting a dataset with only subid and IPAdress
ip <- bot_check %>% 
  select(subid, IPAddress)

#identifying the repeat IP addresses
repeat_ips <- ip$IPAddress[duplicated(ip$IPAddress)]

#getting the corresponding subids
bot_check %>% 
  select(subid, IPAddress, LocationLatitude, LocationLongitude) %>% 
  filter(IPAddress %in% c("24.241.223.182", "72.79.119.56", "108.230.124.237", "172.97.7.163", "67.236.228.7", "68.190.36.43"))

#removing the subids from the overall dataset that has already been cleaned to remove people who did not correctly complete the PT narrative task
no_bots <- wide_data %>% 
  filter(!subid %in% c(96, 99, 166, 167, 171, 239, 265, 345, 613, 758, 778, 779))

no_bots <- no_bots[-c(1), ] 
#Data cleaning
clean_data <- no_bots %>% 
  ## drop two MFQ items that aren't actually the survey - 6, 22 in each
select(-MFQSelf_6, -MFQSelf_22, -MFQTrump_6, -MFQTrump_22, -MFQClin_6,
       -MFQClin_22, -MFQTarg_6, -MFQTarg_22) %>% 
  ## dropping PANAS and exploratory items for this study to make data more manageable
  select(-c(PANAS1_1:PANAS1_20, PANAS2_1:PANAS2_20, 
            gender_writein, race_writein, birth_writein, race_writein, 
            language_writein, raise_writein)) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  ### Wrangling data to get MFQ for self, MFQ to targ, MFQ for stereotype, column for candidate, average of IG identification
  gather("MFQ_Type", "MFQ_Score", MFQSelf_1:MFQTarg_32) %>% 
  separate(.,MFQ_Type, c("MFQ_Type", "MFQ_Number"),"\\_") %>% 
  spread(MFQ_Type, MFQ_Score) %>% 
  gather("IG_Type", "IG_Score", IG_Clin_1:IG_Trump_14) %>% 
  separate(.,IG_Type, c("Drop", "IG_Type", "IG_Number"),"\\_") %>% 
  filter(!is.na(IG_Score)) %>% 
  group_by(subid) %>% 
  #average of in-group identification for each subject
  #making candidate they voted for a factor
  mutate(Cand_votedfor = ifelse(IG_Type == "Clin", 1, 
                                ifelse(IG_Type == "Trump", 0, NA))) %>% 
  gather("Day_key", "Day_content", Day_Clin_In_PT:Day_Trump_In_C) %>% 
  mutate(Day_key = as.factor(Day_key)) %>% 
  filter(!is.na(Day_content)) %>% 
  mutate(inoutgroup = fct_collapse(Day_key, 
                                   Ingroup = c("Day_Clin_In_C", 
                                                "Day_Clin_In_PT", 
                                                "Day_Trump_In_C", 
                                                "Day_Trump_In_PT"), 
                                   Outgroup = c("Day_Clin_Out_C", 
                                                "Day_Clin_Out_PT",
                                                "Day_Trump_Out_C", 
                                                "Day_Trump_Out_PT")),
         PT = fct_collapse(Day_key,
                           PT = c("Day_Clin_In_PT",
                                  "Day_Trump_In_PT",
                                  "Day_Clin_Out_PT",
                                  "Day_Trump_Out_PT"),
                           control = c("Day_Clin_In_C",
                                       "Day_Trump_In_C",
                                       "Day_Clin_Out_C",
                                       "Day_Trump_Out_C")),
         par_cand = fct_collapse(Day_key,
                                  Clinton = c("Day_Clin_In_PT",
                                           "Day_Clin_Out_PT",
                                           "Day_Clin_In_C",
                                           "Day_Clin_Out_C"),
                                  Trump = c("Day_Trump_In_PT",
                                            "Day_Trump_Out_PT",
                                            "Day_Trump_In_C",
                                            "Day_Trump_Out_C")),
         targ_cand = fct_collapse(Day_key,
                                  Clinton = c("Day_Clin_In_PT",
                                              "Day_Clin_In_C",
                                              "Day_Trump_Out_PT",
                                              "Day_Trump_Out_C"),
                                  Trump = c("Day_Clin_Out_PT",
                                            "Day_Clin_Out_C",
                                            "Day_Trump_In_PT",
                                            "Day_Trump_In_C")))

clean_data[,1:31] <- sapply(clean_data[,1:31],as.numeric)
clean_data[,34:36] <- sapply(clean_data[,34:36],as.numeric)

clean_data2 <- clean_data %>%
  mutate(IG_ave = mean(IG_Score)) %>% 
  filter(!is.na(IG_ave)) %>% 
  select(-Drop) %>% 
  #effects coding for group with ingroup = .5 and outgorup = -.5, for PT .5 = PT and Control = -.5
  mutate(inoutgroup_effects = ifelse(inoutgroup == "Ingroup", .5,
                                     ifelse(inoutgroup == "Outgroup", -.5, NA)),
         PT_effects = ifelse(PT == "PT", .5, 
                             ifelse(PT == "control", -.5, NA)),
         targ_cand = ifelse(targ_cand == "Clinton", 1, 
                            ifelse(targ_cand == "Trump", 2, NA)),
         MFQStereo = ifelse(par_cand == "Clinton", MFQClin, 
                            ifelse(par_cand == "Trump", MFQTrump, NA))) %>% 
  #grand mean centering MFQ for self
  mutate(MFQSelf_c = MFQSelf - mean(MFQSelf)) %>%  
  #removing people who failed the manipulation check
  filter(targ_cand == 1 & Man_TargVote == 1 | 
           targ_cand == 2 & Man_TargVote == 2) %>%
  select(-Day_content, -Day_key) %>% 
  #effects coding candidate
  mutate(Targ_Cand_effectscoded = ifelse(targ_cand == "1", .5, 
                                         ifelse(targ_cand == "2", -.5, NA)),
         MFQStereo_c = MFQStereo - mean(MFQStereo, na.rm = TRUE))

#for some reason, this wouldn't work in the piping above, so had to hard code it
#grand mean centering for ingroup identification
clean_data2$ident_c <- clean_data2$IG_ave - mean(clean_data2$IG_ave, na.rm = TRUE)
clean_data2$Gender <- as.factor(clean_data2$Gender)
levels(clean_data2$Gender) <- c("Male", "Female", "Other")
clean_data2$Race <- as.factor(clean_data2$Race)
levels(clean_data2$Race) <- c("American Indian/Native Alaskan", 
                             "Asian", 
                             "Black",
                             "Latinx",
                             "Middle Eastern",
                             "Caucasian",
                             "Multiracial",
                             "Other")

#data with just the variables for analysis for stereotyping
stereo_analysis <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf_c, MFQStereo_c, MFQTarg, ident_c, PT_effects, 
         inoutgroup_effects, Man_PT, par_cand) %>%
  unique() %>% 
  na.omit()
```

```{r data import and cleaning F1, include = FALSE}
#Reading in the data
pptnpf1 <- read.csv("PPTNPF1_clean_nopt.csv", header = TRUE) 

correct_mfq <- pptnpf1 %>% 
  select(-MFQ_Self_Check1, -MFQ_Self_Check2, -MFQ_Targ_Check1, -MFQ_Targ_Check2)

#Getting the data in long-format
pptnpf1_comb <-  correct_mfq %>% 
  dplyr::select(Subject, Condition, Gender, Race, Age, Issue_agreement, 
                Identification, ManCheck, 
                MFQSelf.=MFQ_Self_1:MFQ_Self_23, 
                MFQTarg.=MFQ_Targ_1:MFQ_Targ_23) %>% 
  gather(MFQType, MFQResponse, MFQSelf.1:MFQTarg.20, factor_key = TRUE) %>% 
  separate(.,MFQType,c("MFQ","number"),"\\.") %>% 
  spread(.,MFQ, MFQResponse) %>% 
  mutate_each(.,funs(as.numeric(as.character(.)))) %>% 
  group_by(Subject)



#Making each value the right type (numeric or factor) and centered
pptnpf1_comb$MFQSelf_c <- as.numeric(pptnpf1_comb$MFQSelf - 
                                       mean(pptnpf1_comb$MFQSelf, na.rm = TRUE))
pptnpf1_comb$Identification_c <- as.numeric(pptnpf1_comb$Identification - 
                                              mean(pptnpf1_comb$Identification, 
                                                   na.rm = TRUE))
pptnpf1_comb$Condition <- as.factor(pptnpf1_comb$Condition)
pptnpf1_comb$Gender <- as.factor(pptnpf1_comb$Gender)
pptnpf1_comb$Race <- as.factor(pptnpf1_comb$Race)
pptnpf1_comb$Age <- as.numeric(pptnpf1_comb$Age)
pptnpf1_comb <- na.omit(pptnpf1_comb)

#Adding contrast codes for our categorical variable
PRWvPB <- c(1, -1, -1, 3) 
PRvW <- c(-1, -1, 2, 0)  
PvR <- c(-1, 1, 0, 0) 
ConCodes <- cbind(PRWvPB, PRvW, PvR)
contrasts(pptnpf1_comb$Condition) <- ConCodes
contrasts(pptnpf1_comb$Condition)
```

```{r data import and cleaning F2, include = FALSE}

```

# Stereotyping analysis: Initial Study

```{r stereo analysis}
#model
projmodel_stereo_dem <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c +
                                    (MFQSelf_c|subid), 
                                 data = stereo_analysis)

#results
tab_model(projmodel_stereo_included,
          title = "Projection moderated by stereotyping")

```

```{r}
describe(stereo_analysis$ident_c)
describe(stereo_analysis$inoutgroup_effects)

initial_study_3way <- effect(term = "MFQSelf_c:inoutgroup_effects:ident_c", 
                           xlevels = list(ident_c = c(-1.8, 0, 1.8), 
                                         inoutgroup_effects = c(-.5,.5)), 
                           mod = projmodel_stereo_included)

initial_study_3way <- as.data.frame(initial_study_3way)

initial_study_3way$Group <- as.factor(initial_study_3way$inoutgroup_effects)
initial_study_3way$Identification <- as.factor(initial_study_3way$ident_c)

ident_label <- c("-1.8" = "Low identification \n (1 SD below)", 
                 "0" = "Average identification",
                 "1.8" = "High identificatiion \n(1 SD above)")

```

```{r three-way plot BW}
ggplot(initial_study_3way, aes(MFQSelf_c, 
                             fit, 
                             group = Group, 
                             color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black", 
              aes(linetype = Group)) +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                   "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by in-group identification and group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r main effect group plot set-up, include = FALSE}
# getting the information for the main effect of group
initial_study_main_group <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = projmodel_stereo_included)

initial_study_main_group <- as.data.frame(initial_study_main_group)

initial_study_main_group$Group <- as.factor(initial_study_main_group$inoutgroup_effects)
```

```{r main effect group plot BW}
ggplot(initial_study_main_group, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

These results demonstrate that our significant three-way interaction from before is no longer significant, but the main effect of group identification still is significant and still shows counter projection. The three-way is not significant because, regardless of in-group identification, people are still counter projecting to the same extent with their out-group and projecting normally with their in-group.

## With political affiliation as moderator

```{r stereo analysis by cand}
#model
is_cand <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c * par_cand +
                                    (MFQSelf_c|subid), 
                                 data = stereo_analysis)

#results
tab_model(is_cand,
          title = "Projection moderated by stereotyping")

```

When we include who the participant voted for with stereotyping as well, we still have the main effect from above. Now, the interaction between target group and in-group identification is significant. There is also an interaction between target group (in or out) and who the participant voted for. However, an interaction between target group, degree of in-group identification, and who they voted for is not significant. There are other significant interactions including stereotyping, but, since we only included it as a moderator to see if the relationship persisted, I didn't go through them thoroughly.

```{r is group by cand}
levels(stereo_analysis$par_cand)
# getting the information for the main effect of group
is_group_cand <- effect(term = "MFQSelf_c:inoutgroup_effects:par_cand", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5),
                                            par_cand = c("Clinton", "Trump")), 
                             mod = is_cand)

is_group_cand <- as.data.frame(is_group_cand)

is_group_cand$Group <- as.factor(is_group_cand$inoutgroup_effects)


```

```{r is group by cand}
ggplot(is_group_cand, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  facet_wrap(~par_cand)+
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```   

Clinton supporters counter project and Trump supporters do not. I've checked this a lot and it seems to be correct, I must have messed up in my first year when I analyzed it...


```{r stereo cand 3way set-up}
describe(stereo_analysis$ident_c)
describe(stereo_analysis$inoutgroup_effects)

is_3way_cand <- effect(term = "MFQSelf_c:inoutgroup_effects:ident_c", 
                           xlevels = list(ident_c = c(-1.78, 0, 1.78), 
                                         inoutgroup_effects = c(-.5,.5)), 
                           mod = is_cand)

is_3way_cand <- as.data.frame(is_3way_cand)

is_3way_cand$Group <- as.factor(is_3way_cand$inoutgroup_effects)
is_3way_cand$Identification <- as.factor(is_3way_cand$ident_c)

ident_label <- c("-1.78" = "Low identification \n (1 SD below)", 
                 "0" = "Average identification",
                 "1.78" = "High identificatiion \n(1 SD above)")

```

```{r three-way stereo cand}
ggplot(is_3way_cand, aes(MFQSelf_c, 
                             fit, 
                             group = Group, 
                             color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black", 
              aes(linetype = Group)) +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                   "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by in-group identification and group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r main effect group plot set-up cand, include = FALSE}
# getting the information for the main effect of group
is_group_cand <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = is_cand)

is_group_cand <- as.data.frame(is_group_cand)

is_group_cand$Group <- as.factor(is_group_cand$inoutgroup_effects)
```

```{r main effect group plot BW cand}
ggplot(is_group_cand, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

# MFQ sub areas

```{r mfq subscales}
#separating MFQ into binding and individualizing subscales
mfq_binding <- clean_data2 %>% 
  filter(MFQ_Number %in% c("3", "4", "5", "9", "10", "11", "14", "15", "16", 
                           "19", "20", "21", "25", "26", "27", "30", "31", "32")) %>%
  select(subid, MFQ_Number, MFQTarg, MFQSelf_c, MFQStereo_c, inoutgroup_effects, ident_c, par_cand) %>% 
  unique() %>% 
  na.omit()

mfq_individual <- clean_data2 %>% 
  filter(MFQ_Number %in% c("1", "2", "7", "8", "12", "13", "17", "18", "23", 
                           "24", "28", "29")) %>%
  select(subid, MFQ_Number, MFQTarg, MFQSelf_c, MFQStereo_c, inoutgroup_effects, ident_c, par_cand) %>% 
  unique() %>% 
  na.omit()
```

## Initial Study

### Binding
```{r mfq binding model}
#model
is_mfqbinding <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c +
                                    (MFQSelf_c|subid), 
                                 data = mfq_binding)

#results
tab_model(is_mfqbinding,
          title = "Projection moderated by stereotyping for binding morals")
```

```{r 3 way mfq binding set up}
describe(mfq_binding$ident_c)

is_binding_3way <- effect(term = "MFQSelf_c:inoutgroup_effects:ident_c", 
                           xlevels = list(ident_c = c(-1.78, 0, 1.78), 
                                         inoutgroup_effects = c(-.5,.5)), 
                           mod = is_mfqbinding)

is_binding_3way <- as.data.frame(is_binding_3way)

is_binding_3way$Group <- as.factor(is_binding_3way$inoutgroup_effects)
is_binding_3way$Identification <- as.factor(is_binding_3way$ident_c)

ident_label <- c("-1.78" = "Low identification \n (1 SD below)", 
                 "0" = "Average identification",
                 "1.78" = "High identificatiion \n(1 SD above)")

```

```{r 3way mfq binding plot}
ggplot(is_binding_3way, aes(MFQSelf_c,
                             fit, 
                             group = Group,
                             color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black", 
              aes(linetype = Group)) +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                   "dashed")) +
  theme_minimal() +
  labs(title = "Projection of binding morals predicted by in-group identification and group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r binding main effectgroup plot set-up, include = FALSE}
# getting the information for the main effect of group
is_binding_group <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = is_mfqbinding)

is_binding_group <- as.data.frame(is_binding_group)

is_binding_group$Group <- as.factor(is_binding_group$inoutgroup_effects)
```

```{r binding main effect group plot BW}
ggplot(is_binding_group, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection of binding morals predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

### Binding including participant vote

```{r mfq binding model cand}
#model
is_mfqbinding_cand <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c * par_cand +
                                    (MFQSelf_c|subid), 
                                 data = mfq_binding)

#results
tab_model(is_mfqbinding_cand,
          title = "Projection moderated by stereotyping for binding morals")
```

Main effect of target group is still significant. Who participants voted for is marginal (.050). The interaction between target group and identification is still significant. The interaction between target group, identification, and who they voted for is not significant.

```{r binding group by cand}
# getting the information for the main effect of group
bind_group_cand <- effect(term = "MFQSelf_c:inoutgroup_effects:par_cand", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5),
                                            par_cand = c("Clinton", "Trump")), 
                             mod = is_mfqbinding_cand)

bind_group_cand <- as.data.frame(bind_group_cand)

bind_group_cand$Group <- as.factor(bind_group_cand$inoutgroup_effects)


```

```{r binding group by cand}
ggplot(bind_group_cand, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  facet_wrap(~par_cand)+
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
``` 

### Individualizing

```{r mfq individual model}
#model
is_mfqindividual <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c +
                                    (MFQSelf_c|subid), 
                                 data = mfq_individual)

#results
tab_model(is_mfqindividual,
          title = "Projection moderated by stereotyping for individualizing morals")
```


The main effect of target group is still significant. The interaction between target group and identification is no longer significant, but I plotted it just to show the difference.

```{r 3 way mfq individual set up}
describe(mfq_individual$ident_c)

is_indiv_3way <- effect(term = "MFQSelf_c:inoutgroup_effects:ident_c", 
                           xlevels = list(ident_c = c(-1.78, 0, 1.78), 
                                         inoutgroup_effects = c(-.5,.5)), 
                           mod = is_mfqindividual)

is_indiv_3way <- as.data.frame(is_indiv_3way)

is_indiv_3way$Group <- as.factor(is_indiv_3way$inoutgroup_effects)
is_indiv_3way$Identification <- as.factor(is_indiv_3way$ident_c)

ident_label <- c("-1.78" = "Low identification \n (1 SD below)", 
                 "0" = "Average identification",
                 "1.78" = "High identificatiion \n(1 SD above)")

```

```{r 3way mfq individual plot}
ggplot(is_indiv_3way, aes(MFQSelf_c, 
                             fit, 
                             group = Group, 
                             color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black", 
              aes(linetype = Group)) +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                   "dashed")) +
  theme_minimal() +
  labs(title = "Projection of individualizing morals predicted by in-group identification and group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r individual main effectgroup plot set-up, include = FALSE}
# getting the information for the main effect of group
is_indiv_group <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = is_mfqindividual)

is_indiv_group <- as.data.frame(is_indiv_group)

is_indiv_group$Group <- as.factor(is_indiv_group$inoutgroup_effects)
```

```{r indiv main effect group plot BW}
ggplot(is_indiv_group, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection of individualizing morals predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

### Individualizing including participant vote

```{r mfq individual model cand}
#model
is_mfqindividual_cand <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c * par_cand +
                                    (MFQSelf_c|subid), 
                                 data = mfq_individual)

#results
tab_model(is_mfqindividual_cand,
          title = "Projection moderated by stereotyping for individual morals")
```


Main effect of target group is still significant. The main effect of who participants voted for is marginal (.077). The interactions between target group and identification  between target group and who participants voted for, and target group, identification, and who participants voted for are all not significant.

```{r individual main effectgroup plot set-up with cand, include = FALSE}
# getting the information for the main effect of group
is_indiv_group_cand <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = is_mfqindividual_cand)

is_indiv_group_cand <- as.data.frame(is_indiv_group_cand)

is_indiv_group_cand$Group <- as.factor(is_indiv_group_cand$inoutgroup_effects)
```

```{r indivi main effect group plot with cand}
ggplot(is_indiv_group_cand, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection of individualizing morals predicted by group membership",
       subtitle = "Controlling for stereotyping",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

## Follow-up 1

```{r f1 mfq subscales}
#separating MFQ into binding and individualizing subscales
f1_mfq_binding <- pptnpf1_comb %>% 
  filter(number %in% c("3", "4", "5", "9", "10", "11", "14", "15", "16", 
                           "20", "21", "22")) %>%
  select(Subject, number, Condition, MFQSelf_c, Identification_c, Gender, Race, MFQTarg) %>% 
  unique() %>% 
  na.omit()

f1_mfq_individual <- pptnpf1_comb %>% 
  filter(number %in% c("1", "2", "7", "8", "12", "13", "18", "19")) %>%
  select(Subject, number, Condition, MFQSelf_c, Identification_c, Gender, Race, MFQTarg) %>% 
  unique() %>% 
  na.omit()
```

### Binding

```{r f1 binding model}
f1_binding <- lmer(MFQTarg ~ MFQSelf_c*Identification_c*Condition + 
                              (MFQSelf_c|Subject), 
                            data = f1_mfq_binding, na.action = na.omit)

tab_model(f1_binding,
          title = "Effects of predictors and interactions on projection of binding morals")
```

## Plot of three-way interaction

```{r f1 binding three way,include = FALSE, echo = FALSE}
#Creating label for in-group identification so it can be treated like a categorical variable in the plot
describe(f1_mfq_binding$Identification_c)
Ident_label <- c("-1.19" = "Low identification \n (1 SD below)",
                 "0" = "Average \n identification",
                 "1.19" = "High identification \n (1 SD above)")

#Getting summary stats to plot
f1_binding_summary_3way <-summary(lsmeans(f1_binding , 
                               ~MFQSelf_c|Identification_c|Condition, 
                               at = list (MFQSelf_c = c(-3:3), 
                                          Identification_c = c(-1.19, 0, 1.19))))
```


```{r Three-way BW model f1 binding}
#running the plot

ggpreview <- function(...) {
  fname <- tempfile(fileext = ".png")
  ggsave(filename = fname, ...)
  system2("open", fname)
  invisible(NULL)
}

knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 

ggplot(f1_binding_summary_3way, aes(x = MFQSelf_c, 
                         y = lsmean, 
                         group = as.factor(Condition))) + 
  facet_grid(.~Identification_c,
             labeller = labeller(Identification_c = Ident_label)) + 
  geom_line(size = .7, aes(linetype = Condition)) +
  xlab("MFQ responses for self") + 
  ylab("MFQ responses for target") + 
  scale_linetype_manual("Issue polarization", 
                        breaks = c(1,2,3,4), 
                        labels = c ("Political\ncandidate",
                                   "Racial\ndisadvantage",
                                   "Marijuana\nlegalization",
                                   "Peanut\nbutter"),
                        values = c("solid",
                                   "twodash", 
                                   "dotted", 
                                   "dashed")) + 
  ggtitle("Projection predicted by identification and issue polarization") +
  theme_minimal(base_size = 13) +
  theme(legend.text = element_text(size = 10),
        legend.key.width = unit(1, "cm"),
        legend.position = "bottom")
  
ggpreview(width = 8, height = 6, units = "in")
```

Not much different than the overall, except now average identifiers in the political condition are negatively projecting and people in the racial disadvantage condition who highly identify aren't projecting at all.


```{r f1 binding two-way set-up,include = FALSE, echo = FALSE}
#Get summary stats for plot
f1_binding_sum_cond <-summary(lsmeans(f1_binding, ~MFQSelf_c|Condition, 
                                    at = list(MFQSelf_c = c(-3:3))))
```


```{r f1 binding two-way BW}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 

ggplot(f1_binding_sum_cond, aes(x = MFQSelf_c, 
                              y = lsmean, 
                              group = as.factor(Condition)))+
  geom_line(size = 1, aes(linetype = Condition)) +
  xlab("MFQ responses for self") + 
  ylab("MFQ responses for target") + 
  scale_linetype_manual("Issue polarization", 
                      breaks = c(1,2,3,4),
                      labels = c("Political\ncandidate",
                                  "Racial\ndisadvantage", 
                                  "Marijuana\nlegalization",
                                  "Peanut\nbutter"),
                       values = c("solid",
                                   "twodash", 
                                   "dotted", 
                                   "dashed")) +
  ggtitle("Effect of issue polarization on projection with out-group targets") +
  theme_minimal(base_size = 13) +
  theme(legend.text = element_text(size = 10),
        legend.key.width = unit(1.2, "cm"))


ggpreview(width = 8, height = 6, units = "in")
```
Only difference is now there is counter projection in the political candidate condition.

```{r f1 binding ident set-up, include = FALSE}
#information to plot main effect of in-group identification
describe(f1_mfq_binding$Identification_c)

f1_binding_ident <- effect(term ="MFQSelf_c:Identification_c", 
                             xlevels = list(Identification_c = c(-1.19, 0, 1.19)), 
                             mod = f1_binding)

f1_binding_ident <- as.data.frame(f1_binding_ident)

f1_binding_ident$Identification <- as.factor(f1_binding_ident$Identification_c)
```

```{r f1 binding ident plot}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 

ggplot(f1_binding_ident, aes(MFQSelf_c, 
                               fit, 
                               group = Identification)) +
  geom_line(aes(linetype = Identification), size = .7) +
  scale_linetype_manual("Identification", 
                       breaks = c(-1.19, 0, 1.19), 
                       labels = c ("Low (1 SD below)", 
                                  "Average ", 
                                  "High (1 SD above)"),
                        values = c("solid",
                                   "twodash", 
                                   "dotted")) +
  theme_minimal(base_size = 13) +
  labs(title = "Projection predicted by degree of in-group identification",
       x = "MFQ responses for self",
       y = "MFQ responses for target")

ggpreview(width = 8, height = 6, units = "in")
```
Pretty similiar to the overall model.

### Individualizing

# BFI sub sreas: Follow-up 2

# Political ideology breakdown of counter projection

## Initial Study - already did this above

## Follow-up 1

## Follow-up 2

# Demographic differences in counter projection

## Initial Study - Gender & race

```{r stereo analysis with race}
dem_analysis <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf_c, MFQStereo_c, MFQTarg, ident_c, PT_effects, 
         inoutgroup_effects, par_cand, Race) %>%
  unique() %>% 
  na.omit()

#model
projmodel_stereo_race <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c * Race +
                                    (MFQSelf_c|subid), 
                                 data = dem_analysis)

#results
tab_model(projmodel_stereo_race,
          title = "Projection moderated by stereotyping and race")

```

Model is rank deficient, not enough power to check if results differ by race. Could possibly do white vs minorities, but that doesn't feel telling enough.

```{r stereo analysis with gender}
gender_analysis <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf_c, MFQStereo_c, MFQTarg, ident_c, PT_effects, 
         inoutgroup_effects, par_cand, Gender) %>%
  unique() %>% 
  na.omit()

#model
projmodel_stereo_gender <- lmer(MFQTarg ~ MFQSelf_c * MFQStereo_c *
                                    inoutgroup_effects * ident_c * Gender +
                                    (MFQSelf_c|subid), 
                                 data = gender_analysis)

#results
tab_model(projmodel_stereo_gender,
          title = "Projection moderated by stereotyping and gender")

```

Gender does not moderate the results.

## Follow-up 1 - Gender

## Follow-up 1 - Race

## Follow-up 2 - Gender

## Follow-up 2 - Race

# Downstream outcomes impacted by counter projection - Initial Study

# Look at how they respond for in-group to address demand? Does this mean looking at whether they are approve or disapprove of the condition in F1 and F2?

# Alphas for the MFQ