---
title: "Exploratory BFI code"
author: "Kathryn Denning"
date: "12/12/2019"
output: html_document
---

````{r setup data import and cleaning, echo = FALSE, warning = FALSE, message=FALSE, error=FALSE}
# Cleaning
## import data

#install.packages("rio")
#install.packages("here")
#install.packages("tidyverse")
#install.packages("magrittr")
#install.packages("janitor")
#install.packages("lme4")
#install.packages("psy")
#install.packages("irr")
#install.packages("emmeans")
#install.packages("sjPlot")
#install.packages("effects")
library(rio)
library(here)
library(magrittr)
library(janitor)
library(lme4)
library(psy)
library(irr)
library(dplyr)
library(ggeffects)
library(sjPlot)
library(tidyverse)
library(psych)
library(emmeans)
library(effects)

#Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

#Data after manually removing participants who did not correctly complete the PT manipulation
npf2_wide <- import("npf2_wide_ptclean2.xlsx") 

#dropping second row that had full questions and overwriting because don't want that for analyses
npf2_wide <- npf2_wide[-c(1),,drop=F] 

#reverse coding
npf2_wide_recode <- npf2_wide %>% 
     mutate_at(c("bfi2xsh_self_quiet", "bfi2xsh_self_rude", 
                 "bfi2xsh_self_disorg", "bfi2xsh_self_taskdiff",
                 "bfi2xsh_self_stable", "bfi2xsh_self_abstract",
                 "bfi2xsh_self_risk", "bfi2xsh_self_uses",
                 "bfi2xsh_targ_quiet", "bfi2xsh_targ_rude",
                 "bfi2xsh_targ_rude", "bfi2xsh_targ_disorg",
                 "bfi2xsh_targ_taskdiff", "bfi2xsh_targ_stable",
                 "bfi2xsh_targ_abstract", "bfi2xsh_targ_risk",
                 "bfi2xsh_targ_uses"), 
               list(~dplyr::recode(., `1`= 5, `2`= 4, `3` = 3, `4` = 2, `5` = 1)))


# Cleaning and putting data in long-format
npf2_clean <- npf2_wide_recode %>% 
  # Dropping open-ended questions
  select(-c(pt_narr_pol, pt_narr_race, pt_narr_thirdpart, pt_narr_weed)) %>% 
  # Making all character variables numeric
  mutate_if(is.character,as.numeric) %>% 
  # Putting responses for personality items into long format for participant and target
  pivot_longer(c(bfi2xsh_self_quiet:bfi2xsh_self_rules, 
           bfi2xsh_targ_quiet:bfi2xsh_targ_rules),
           names_sep = "_",
           names_to = c("drop1", "bfi2xsh_type", "bfi2xsh_qtype")) %>% 
  pivot_wider(names_from = bfi2xsh_type, values_from = value) %>% 
  # Putting responses on other items (conditon, identification, liberal and conservative ratings) into long-format
  pivot_longer(c(opin_pol:check_thirdpart),
               names_sep = "_",
               names_to = c("question", "condition")) %>% 
  na.omit() %>% 
  pivot_wider(names_from = question, values_from = value) %>% 
  select(-drop1) %>% 
  # Making a varriable for perceived polarization, making condition a factor variable
  mutate(perceived_polar = abs(lib-cons),
         condition = fct_relevel(condition, 
                                 "pol", 
                                 "race", 
                                 "weed", 
                                 "thirdpart")) %>% 
  # Mean centering continuous predictors
  mutate(self_c = self - mean(self, na.rm = TRUE),
         ident_c = ident - mean(ident, na.rm = TRUE),
         perceived_polar_c = perceived_polar - 
           mean(perceived_polar, na.rm = TRUE)) %>% 
# Removing opin = 5 for when including the condition variable in the analysis 
# Removing it because only want in and out-group for this analysis, this was an error in data collection to have a third option
  filter(opin != 5) %>% 
  # Removing those who responded incorrectly to the manipulation check
  filter(check != 4)
```

## EXPLORATORY CODE: BFI broken down into factors

### Extraversion: quiet, dominant, energy

```{r Extraversion with condition set-up, include = FALSE}
#making the extraversion dataset
extraversion <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_quiet, bfi2xsh_self_leader, bfi2xsh_self_energy, 
         bfi2xsh_targ_quiet, bfi2xsh_targ_leader, bfi2xsh_targ_energy, 
         check_pol, check_race, check_weed, check_thirdpart, opin_pol, 
         lib_pol, lib_race, lib_weed, lib_thirdpart, cons_pol, 
         cons_race, cons_weed, cons_thirdpart) %>% 
  gather("extra_q", "extra_score", bfi2xsh_self_quiet:bfi2xsh_targ_energy) %>% 
  separate(.,extra_q, c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, extra_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()

contrasts(extraversion$condition) <- "contr.helmert"

```

#### Results for extraversion in model with condition

```{r Extraversion condition model}
#contrasts used
contrasts(extraversion$condition) 

#model
extra_randomslopes <- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), 
                           data = extraversion)

#model results
tab_model(extra_randomslopes,
          title = "Extraversion with random slopes and helmert contrasts")
```

##### Plot of two-way interaction between self and condition

```{r extraversion model plot}
ggplot(extraversion, aes(self_c, targ)) +
  geom_smooth(method = "lm", aes(color = condition), se = FALSE) +
  theme_minimal()  +
  labs(title = "Projection of extraversion predicted by condition",
       x = "Extraversion for self",
       y = "Extraversion for target")
```

#### Extraversion in perceived polarization model

```{r extra perceived polar model}
#model for only extraversion
model2_extraversion <- lmer(targ ~ self_c*ident_c*perceived_polar_c + 
                              (self_c|sub_id), data = extraversion)

#results
tab_model(model2_extraversion,
          title = "Model 2 for extraversion only with random slopes")
```

```{r extra perceived polar plot set-up}
#getting data for plot
describe(extraversion$perceived_polar_c)
describe(extraversion$ident_c)

effects_model2_extra <- effect(term="self_c:ident_c:perceived_polar_c", 
                               xlevels= list(ident_c=c(-0.96, 0, 0.96), 
                                             perceived_polar_c = c(-2, 0, 2)), 
                               mod=model2_extraversion)

extra_data <- as.data.frame(effects_model2_extra)

extra_data$Identification<-as.factor(extra_data$ident_c)
extra_data$Polarization<-as.factor(extra_data$perceived_polar_c)

polar_label <- c("-2"="Low Perceived \nPolarization (1 SD Below)", 
                 "0" = "Average Perceived \nPolarization",
                 "2"="High Perceived \nPolarization (1 SD Above)")
```

##### Three-way interaction from perceivd polar model

```{r extra perceived polar plot}
ggplot(extra_data, aes(self_c, 
                       fit, 
                       group = Identification, 
                       color = Identification)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Polarization, labeller = 
               labeller(Polarization=polar_label)) +
  scale_color_discrete("Identification", breaks = c(-0.96, 0, 0.96), 
                       labels =c ("Low (1 SD Below)", 
                                  "Average", 
                                  "High (1 SD Above")) +
  theme_minimal() +
  labs(title = "Projection for extraversion predicted by degree of in-group identification",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")

```

### Agreeableness: Compassionate, rude, best

```{r Agreeable set-up, include = FALSE}
#data for agreeableness
agree <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_rude, bfi2xsh_self_heart, bfi2xsh_self_best, 
         bfi2xsh_targ_rude, bfi2xsh_targ_heart, bfi2xsh_targ_best, 
         check_pol, check_race, check_weed, check_thirdpart, opin_pol, 
         lib_pol, lib_race, lib_weed, lib_thirdpart, cons_pol, 
         cons_race, cons_weed, cons_thirdpart) %>% 
  gather("extra_q", "extra_score", bfi2xsh_self_rude:bfi2xsh_targ_best) %>% 
  separate(.,extra_q,c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, extra_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()
  
contrasts(agree$condition) <- "contr.helmert"
```

#### Results for agreeableness in model with condition

```{r Agreeable model}
#contrasts used
contrasts(agree$condition) 

#model
agree_randomslopes<- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), 
                          data = agree)

#results
tab_model(agree_randomslopes,
          title = "Agreeableness with random slopes and helmert contrasts")
```

##### Plot of self interacting with condition

```{r agreeable plot 1}
#getting the information for the plot of self interacting with condition
effects_agree_main <- effect(term="self_c:condition", xlevels= list(condition=c("pol","race","thirdpart","weed")), mod=agree_randomslopes)

effects_agree_main_data <- as.data.frame(effects_agree_main)

#plot of self interacting with condition
ggplot(effects_agree_main_data, aes(self_c, fit)) +
  geom_smooth(method = "lm", aes(color = condition)) +
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill = condition), alpha = .2) +
  theme_minimal() +
  labs(title = "Projection of agreeableness predicted by condition",
       subtitle = "Contrast between politics and weed is significant",
       x = "Agreeableness for self",
       y = "Agreeableness ratings for target")
```

##### Plot of three-way interaction

```{r agreeable plot 2}
#getting information for three-way plot
describe(agree$ident_c)

effects_agree <- effect(term="self_c:ident_c:condition", 
                        xlevels= list(ident_c=c(-0.97, 0, 0.97), 
                                      condition=c("pol",
                                                  "race",
                                                  "thirdpart",
                                                  "weed")), 
                        mod=agree_randomslopes)

effects_agree_data <- as.data.frame(effects_agree)

effects_agree_data$Identification<-as.factor(effects_agree_data$ident_c)

agree_ident_label <- c("-0.97"="Low Identification \n(1 SD Below)", 
                       "0" = "Average \nIdentification",
                       "0.97"="High Identification \n(1 SD Above)")

#three-way interaction
ggplot(effects_agree_data, aes(self_c, fit)) +
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill = condition), alpha = .3) +
  facet_wrap(~Identification, 
             labeller = labeller(Identification=agree_ident_label)) +
  geom_smooth(method = "lm", aes(color = condition)) +
  theme_minimal() +
  labs(title = "Projection of agreeableness predicted by \nin-group identification and condition",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")

```

#### Model for agreeableness in model with perceived polarization

```{r agreeable perceived polar model}
#model
model2_agree<- lmer(targ ~ self_c*ident_c*perceived_polar_c + (self_c|sub_id), 
                    data = agree)
#results
tab_model(model2_agree,
          title = "Model 2 for agreeableness only with random slopes")
```

```{r agreeable perceived polar plot set-up}
#getting data for the plot
describe(agree$perceived_polar_c)
describe(agree$ident_c)

effects_model2_agree <- effect(term="self_c:ident_c:perceived_polar_c", 
                               xlevels= list(ident_c=c(-0.96, 0, 0.96), 
                                             perceived_polar_c = c(-2, 0, 2)), 
                               mod=model2_agree)

effects_agree <- as.data.frame(effects_model2_agree)

effects_agree$Identification<-as.factor(effects_agree$ident_c)
effects_agree$Polarization<-as.factor(effects_agree$perceived_polar_c)

polar_label <- c("-2"="Low Perceived \nPolarization (1 SD Below)", 
                 "0" = "Average Perceived \nPolarization",
                 "2"="High Perceived \nPolarization (1 SD Above)")
```

##### Plot for three-way interaction

```{r agreeable perceived polar plot}
ggplot(effects_agree, aes(self_c, 
                          fit, 
                          group = Identification, 
                          color = Identification)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Polarization, labeller = 
               labeller(Polarization=polar_label)) +
  scale_color_discrete("Identification", breaks = c(-0.96, 0, 0.96), 
                       labels =c ("Low (1 SD Below)", "Average", 
                                  "High (1 SD Above")) +
  theme_minimal() +
  labs(title = "Projection for agreeableness predicted by degree of in-group identification",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")
```

### Conscientiousness: disorganized, taskdiff, reliable

```{r consc set-up, include = FALSE}
#getting the data for conscientiousness
consc <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_disorg, bfi2xsh_self_taskdiff, bfi2xsh_self_count, 
         bfi2xsh_targ_disorg, bfi2xsh_targ_taskdiff, bfi2xsh_targ_count, 
         check_pol, check_race, check_weed, check_thirdpart, opin_pol, lib_pol, 
         lib_race, lib_weed, lib_thirdpart, cons_pol, cons_race, 
         cons_weed, cons_thirdpart) %>% 
  gather("cons_q", "cons_score", bfi2xsh_self_disorg:bfi2xsh_targ_count) %>% 
  separate(.,cons_q,c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, cons_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()

contrasts(consc$condition) <- "contr.helmert"
```

#### Results for conscientiousness and condition model

```{r consc model}
#contrasts used
contrasts(consc$condition) 

#model run
consc_randomslopes <- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), data = consc)

#results
tab_model(consc_randomslopes ,
          title = "Conscientiousness with random slopes and helmert contrasts")
```

#### Plot of projection by condition for conscientiousness

```{r cons plot by cond}
#getting the information for the plot of self interacting with condition
effects_cons_main <- effect(term="self_c:condition", xlevels= list(condition=c("pol","race","thirdpart","weed")), mod=consc_randomslopes)

effects_cons_main_data <- as.data.frame(effects_cons_main)

#plot of self interacting with condition
ggplot(effects_cons_main_data, aes(self_c, fit)) +
  geom_smooth(method = "lm", aes(color = condition)) +
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill = condition), alpha = .2) +
  theme_minimal() +
  labs(title = "Projection of conscientiousness predicted by condition",
       subtitle = "Contrast between politics and weed is significant",
       x = "Conscientiousness for self",
       y = "Conscientiousness for target")
```


#### Results for conscientiousness and perceived polarization model

```{r consc perceived pol model}
#model
model2_consc<- lmer(targ ~ self_c*ident_c*perceived_polar_c + (self_c|sub_id), 
                    data = consc)

#results
tab_model(model2_consc,
          title = "Model 2 for conscientiousness only with random slopes")
```

```{r consc perceived pol plot set-up}
# getting the data for the plot
describe(consc$perceived_polar_c)
describe(consc$ident_c)

effects_model2_consc <- effect(term="self_c:ident_c:perceived_polar_c", 
                               xlevels= list(ident_c=c(-0.96, 0, 0.96), 
                                             perceived_polar_c = c(-2, 0, 2)), 
                               mod=model2_consc)

effects_consc <- as.data.frame(effects_model2_consc)

effects_consc$Identification<-as.factor(effects_consc$ident_c)
effects_consc$Polarization<-as.factor(effects_consc$perceived_polar_c)

polar_label <- c("-2"="Low Perceived \nPolarization (1 SD Below)", 
                 "0" = "Average Perceived \nPolarization",
                 "2"="High Perceived \nPolarization (1 SD Above)")
```

##### Three-way plot

```{r plot of three-way perceived pol consc}
#three-way plot to look at directionality even though not significant for overall understnding of how the effects change at the factor level of BFI
ggplot(effects_consc, aes(self_c, 
                          fit, 
                          group = Identification, 
                          color = Identification)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Polarization, labeller = 
               labeller(Polarization=polar_label)) +
  scale_color_discrete("Identification", breaks = c(-0.96, 0, 0.96), 
                       labels =c ("Low (1 SD Below)", 
                                  "Average", 
                                  "High (1 SD Above")) +
  theme_minimal() +
  labs(title = "Projection for conscientiousness predicted by degree of in-group identification",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")
```

### Negative Emotion: Worry, Depressed, Stable

```{r neg emo set-up, include = FALSE}
#getting data for negative emotion
negemo <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_worry, bfi2xsh_self_depress, bfi2xsh_self_stable, 
         bfi2xsh_targ_worry, bfi2xsh_targ_depress, bfi2xsh_targ_stable, 
         check_pol, check_race, check_weed, check_thirdpart, opin_pol, 
         lib_pol, lib_race, lib_weed, lib_thirdpart, cons_pol, cons_race, 
         cons_weed, cons_thirdpart) %>% 
  gather("negemo_q", "negemo_score", 
         bfi2xsh_self_worry:bfi2xsh_targ_stable) %>% 
  separate(.,negemo_q,c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, negemo_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()
  
contrasts(negemo$condition) <- "contr.helmert"
```

#### Results for model including condition

```{r neg emo model}
#contrasts used
contrasts(negemo$condition) 

#model
negemo_randomslopes <- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), data = negemo)

#results
tab_model(negemo_randomslopes,
          title = "Negative emotionality with random slopes and helmert contrasts")
```
#### Plot of projection by condition for negative emotion

```{r negemo plot by cond}
#getting the information for the plot of self interacting with condition
effects_main_negemo <- effect(term="self_c:condition", xlevels= list(condition=c("pol","race","thirdpart","weed")), mod=negemo_randomslopes)

effects_negemo_main_data <- as.data.frame(effects_main_negemo)

#plot of self interacting with condition
ggplot(effects_negemo_main_data, aes(self_c, fit)) +
  geom_smooth(method = "lm", aes(color = condition)) +
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill = condition), alpha = .2) +
  theme_minimal() +
  labs(title = "Projection of negative emotion predicted by condition",
       subtitle = "Contrast between politics and race is significant",
       x = "Negative emotion for self",
       y = "Negative emotion for target")
```

#### Results for model including perceived polarization

```{r neg emo perceived polar model}
#model
model2_negemo <- lmer(targ ~ self_c*ident_c*perceived_polar_c + (self_c|sub_id), 
                      data = negemo)

#results
tab_model(model2_negemo,
          title = "Model 2 for negative emotion only with random slopes")
```

```{r neg emo perceived polar plot set-up}
#getting data for plot
describe(negemo$perceived_polar_c)
describe(negemo$ident_c)

effects_model2_negemo <- effect(term="self_c:ident_c:perceived_polar_c", 
                                xlevels = list(ident_c = c(-0.96, 0, 0.96), 
                                              perceived_polar_c = c(-2, 0, 2)), 
                                mod = model2_negemo)

effects_negemo <- as.data.frame(effects_model2_negemo)

effects_negemo$Identification <- as.factor(effects_negemo$ident_c)
effects_negemo$Polarization <- as.factor(effects_negemo$perceived_polar_c)

polar_label <- c("-2"="Low Perceived \nPolarization (1 SD Below)", 
                 "0" = "Average Perceived \nPolarization",
                 "2"="High Perceived \nPolarization (1 SD Above)")
```

##### Three-way plot

```{r neg emo perceived polar three way plot}
#three-way plot
ggplot(effects_negemo, aes(self_c, 
                           fit, 
                           group = Identification, 
                           color = Identification)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Polarization, labeller = 
               labeller(Polarization = polar_label)) +
  scale_color_discrete("Identification", breaks = c(-0.96, 0, 0.96), 
                       labels = c ("Low (1 SD Below)", "Average", 
                                  "High (1 SD Above")) +
  theme_minimal() +
  labs(title = "Projection for negative emotion predicted by degree of in-group identification",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")
```

### Open-minded: Art, abstract, original

```{r open set-up, include = FALSE}
#cleaning data
open <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_art, bfi2xsh_self_original, bfi2xsh_self_abstract, 
         bfi2xsh_targ_art, bfi2xsh_targ_original, bfi2xsh_targ_abstract, 
         check_pol, check_race, check_weed, check_thirdpart, opin_pol, 
         lib_pol, lib_race, lib_weed, lib_thirdpart, cons_pol, cons_race, 
         cons_weed, cons_thirdpart) %>% 
  gather("open_q", "open_score", bfi2xsh_self_art:bfi2xsh_targ_abstract) %>% 
  separate(.,open_q,c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, open_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()

open <- as.data.frame(open)
  
contrasts(open$condition) <- "contr.helmert"
```

#### Model including condition

```{r open model}
#contrasts used
contrasts(open$condition) 

#model
open_randomslopes <- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), 
                          data = open)

#results
tab_model(open_randomslopes,
          title = "Open mindedness with random slopes and helmert contrasts")

```
#### Plot of projection by condition for openness

```{r opennes plot by cond}
#getting the information for the plot of self interacting with condition
open_plot_cond <- ggeffects::ggpredict(open_randomslopes, terms = c("self_c", "ident_c", "condition"))


#Will make pretty in ggplot if we decide to use this
plot(open_plot_cond)
```

##### Model including perceived polarization

```{r open model perceived pol}
#model
model2_open <- lmer(targ ~ self_c*ident_c*perceived_polar_c + (self_c|sub_id), 
                    data = open)

model2_open
model2_open_sum <- summary(model2_open)
#results
tab_model(model2_open,
          title = "Model 2 for openess only with random slopes")
```
```{r}
open_plot_3way <- ggeffects::ggpredict(model2_open, terms = c("self_c", "ident_c", "perceived_polar_c"))


perceived_label <- c("-2.05164319248826"="Perceived pol at -2.05", 
                 "-1.05164319248826" = "Perceived pol at -1.05",
                 "-0.051643192488263"="Perceived pol at -.05",
                 "0.948356807511737" = "Perceived pol at 0.95",
                 "1.94835680751174" = "Perceived pol at 1.95")

library(ggplot2)
ggplot(open_plot_3way, aes(x = x, y = predicted, color = group)) +
  geom_smooth(method = "lm") +
  facet_wrap(~facet, labeller = labeller(facet = perceived_label)) +
  theme_minimal() +
  scale_color_discrete("", breaks = c(-0.96, 0, 0.96), 
                       labels =c ("Low (1 SD Below)", "Average", 
                                  "High (1 SD Above")) 
#Will make pretty in ggplot if we decide to use this
plot(open_plot_3way)
```         


### Honesty

```{r honesty set-up, include = FALSE}
honest <- npf2_wide %>% 
  select(sub_id, ident_pol, ident_race, ident_weed, ident_thirdpart, 
         bfi2xsh_self_rules, bfi2xsh_self_nodeceive, bfi2xsh_self_uses, 
         bfi2xsh_self_risk, bfi2xsh_targ_rules, bfi2xsh_targ_nodeceive, 
         bfi2xsh_targ_uses, bfi2xsh_targ_risk, check_pol, check_race, 
         check_weed, check_thirdpart, opin_pol, lib_pol, lib_race, lib_weed, 
         lib_thirdpart, cons_pol, cons_race, cons_weed, cons_thirdpart) %>% 
  gather("honest_q", "honest_score", 
         bfi2xsh_self_rules:bfi2xsh_targ_risk) %>% 
  separate(.,honest_q,c("drop","type", "bfi2xsh_qcontent", "drop2"),"\\_") %>% 
  select(-drop, -drop2) %>% 
  spread(type, honest_score) %>% 
  gather("condition", "ident", c(ident_pol, 
                                 ident_race, 
                                 ident_weed, 
                                 ident_thirdpart)) %>% 
  separate(.,condition,c("drop","condition"),"\\_") %>% 
  select(-drop) %>% 
  filter(!is.na(ident)) %>% 
  gather("drop", "check", c(check_pol, 
                            check_race, 
                            check_weed, 
                            check_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(check)) %>% 
  gather("drop1", "lib", c(lib_pol, 
                           lib_race, 
                           lib_weed, 
                           lib_thirdpart)) %>% 
  select(-drop1) %>% 
  filter(!is.na(lib)) %>% 
  gather("drop", "cons", c(cons_pol, 
                           cons_race, 
                           cons_weed, 
                           cons_thirdpart)) %>% 
  select(-drop) %>% 
  filter(!is.na(cons)) %>% 
  mutate(sub_id = as.numeric(sub_id),
         bfi2xsh_qcontent = as.factor(bfi2xsh_qcontent),
         self = as.numeric(self),
         targ = as.numeric(targ),
         ident = as.numeric(ident),
         condition = as.factor(condition),
         lib = as.numeric(lib),
         cons = as.numeric(cons)) %>% 
  mutate(perceived_polar = abs(lib-cons)) %>% 
  mutate(self_c = self - mean(self, na.rm=TRUE),
         ident_c = ident - mean(ident, na.rm=TRUE),
         condition = fct_relevel(condition, "pol", "race", "weed", "thirdpart"),
         perceived_polar_c = perceived_polar - mean(perceived_polar, 
                                                    na.rm=TRUE)) %>% 
  filter(check == 5 | opin_pol != 5) %>% 
   select(-opin_pol) %>% 
  na.omit()
  
contrasts(honest$condition) <- "contr.helmert"
```

#### Honesty model with condition

```{r honesty model condition}
#contrasts used
contrasts(honest$condition) 

#model
honest_randomslopes <- lmer(targ ~ self_c*ident_c*condition + (self_c|sub_id), 
                            data = honest)

#results
tab_model(honest_randomslopes,
          title = "Open mindedness with random slopes and helmert codes")
```

#### Plot of projection by condition for honesty

```{r honesty plot by cond}
#getting the information for the plot of self interacting with condition
effects_main_honest <- effect(term="self_c:condition", xlevels= list(condition=c("pol","race","thirdpart","weed")), mod=honest_randomslopes)

effects_honest_main_data <- as.data.frame(effects_main_honest)

#plot of self interacting with condition
ggplot(effects_honest_main_data, aes(self_c, fit)) +
  geom_smooth(method = "lm", aes(color = condition)) +
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill = condition), alpha = .2) +
  theme_minimal() +
  labs(title = "Projection of honesty predicted by condition",
       x = "Honesty for self",
       y = "Honesty for target")
```

#### Honesty model with perceived polarization

```{r honesty model perceived pol}
#model
model2_honest <- lmer(targ ~ self_c*ident_c*perceived_polar_c + (self_c|sub_id), 
                      data = honest)

#results
tab_model(model2_honest,
          title = "Model 2 for openess only with honest slopes")
```

```{r honesty plot set-up perceived pol}
#getting data for plot
psych::describe(honest$perceived_polar_c)
psych::describe(honest$ident_c)

effects_model2_honest <- effects::effect(term="self_c:ident_c:perceived_polar_c", 
                                xlevels= list(ident_c=c(-0.96, 0, 0.96), 
                                              perceived_polar_c = c(-2, 0, 2)), 
                                mod=model2_honest)

effects_honest <- as.data.frame(effects_model2_honest)

effects_honest$Identification<-as.factor(effects_honest$ident_c)
effects_honest$Polarization<-as.factor(effects_honest$perceived_polar_c)

polar_label <- c("-2"="Low Perceived \nPolarization (1 SD Below)", 
                 "0" = "Average Perceived \nPolarization",
                 "2"="High Perceived \nPolarization (1 SD Above)")
```

##### Three-way plot

```{r honesty perceived pol three way plot}
#three-way plot to look at directionality even though not significant for overall understnding of how the effects change at the factor level of BFI
ggplot2::ggplot(effects_honest, aes(self_c, 
                           fit, 
                           group = Identification, 
                           color = Identification)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Polarization, labeller = 
               labeller(Polarization=polar_label)) +
  scale_color_discrete("Identification", breaks = c(-0.96, 0, 0.96), 
                       labels =c ("Low (1 SD Below)", 
                                  "Average", 
                                  "High (1 SD Above")) +
  theme_minimal() +
  labs(title = "Projection for honesty predicted by degree of in-group identification",
       x = "Personaility ratings for self",
       y = "Personality ratings for target")
```
